### 2018-03-22 Writing/supplementary/Sup1-CharDiff.tex
equation fixes
changed CD equation

\begin{equation}
    CD_{(x,y)} = 1 - \left(\frac{\abs*{\frac{\sum_{i}^{n}\abs{x_{i} - y_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}}\right)
\end{equation}
\noindent Where $n$ is the number of taxa with comparable data and $x_i$ and $y_i$ are each characters states for the characters $x$ and $y$ and the taxa $i$.

@@

For any $n \in [1;\infty)$ and $x_{n}$ and $y_{n} \in (0,1)$ (because the difference between character states is considered as Fitch-like, i.e. the difference between two characters states \texttt{0} and \texttt{8} is equal to $1$ and the difference between two identical character states is equal to $0$):

\begin{equation}
    \label{positive_demo}
    \begin{gathered}
    0 \leq  \abs{x_{n}-y_{n}} \leq 1\\
    0 \leq  \sum_{i=1}^{n}\abs{x_{i}-y_{i}} \leq n\\
    0 \leq  \frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n} \leq 1\\
    0 \leq  \abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}} \leq \frac{1}{2}\\
    0 \leq  \frac{\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}} \leq 1\\
    0 \leq  1 - \left(\frac{\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}}\right) \leq 1\\
    \end{gathered}
\end{equation}

@@

For any $n \in [1;\infty)$ and $x_{n} = y_{n}$ then:
%TG: Is that valid for a demonstration?
\begin{equation}
    \label{identitydemo}
    \begin{aligned}
    \abs{x_{n}-y_{n}} &= 0\\
    \sum_{i}^{n}\abs{x_{i}-y_{i}} &= 0\\
    \frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n} &= 0\\
    \abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}} &= \frac{1}{2}\\
    \frac{\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}} &= 1\\
    1 - \left(\frac{\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}}\right) &= 0\\
    \end{aligned}
\end{equation}

@@

\begin{equation}
    \label{equality_demo}
    \begin{aligned}
    \abs{x_{n}-y_{n}} &= \abs{y_{n}-x_{n}}\\
    \sum_{i}^{n}\abs{x_{i}-y_{i}} &= \sum_{i}^{n}\abs{y_{i}-x_{i}}\\
    \frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n} &= \frac{\sum_{i}^{n}\abs{y_{i}-x_{i}}}{n}\\
    \abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}} &= \abs*{\frac{\sum_{i}^{n}\abs{y_{i}-x_{i}}}{n}-\frac{1}{2}}\\
    \frac{\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}} &= \frac{\abs*{\frac{\sum_{i}^{n}\abs{y_{i}-x_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}}\\
    1 - \left(\frac{\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}}\right) &= 1 - \left(\frac{\abs*{\frac{\sum_{i}^{n}\abs{y_{i}-x_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}}\right)\\
    \end{aligned}
\end{equation}

@@

For any $n, j, b \in [1;\infty)$ and $x_{n}$, $y_{n}$, $z_{n}$ $\in (0,1)$:

\begin{equation}
    \label{subadditivity_demo}
    \begin{aligned}
    CD_{x,y} &\leq CD_{x,z} + CD_{z,y}\\
    \text{if:}\\
    1 - \left(\frac{\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}}\right)
     &\leq 
     1 - \left(\frac{\abs*{\frac{\sum_{k}^{j}\abs{x_{k}-y_{k}}}{j}-\frac{1}{2}}}{\frac{1}{2}}\right) 
     +
     1 - \left(\frac{\abs*{\frac{\sum_{a}^{b}\abs{x_{a}-y_{a}}}{b}-\frac{1}{2}}}{\frac{1}{2}}\right) \\
     \text{then, the opposite is:}\\
    \underbrace{\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}} }_{\in[0,1/2]}
     &\geq 
     \underbrace{\abs*{\frac{\sum_{k}^{j}\abs{x_{k}-y_{k}}}{j}-\frac{1}{2}} }_{\in[0,1/2]}
     +
     \underbrace{\abs*{\frac{\sum_{a}^{b}\abs{x_{a}-y_{a}}}{b}-\frac{1}{2}} }_{\in[0,1/2]} - 2\\
     \text{thus:}\\
     \in[0,\frac{1}{2}] &\geq \in[0,\frac{1}{2}] \in[0,\frac{1}{2}] (-2) \\
     \in[0,\frac{1}{2}] &\geq \in[-2,-1]\\
    \end{aligned}
\end{equation}

>>>>

% \begin{equation}
%     CD_{(x,y)} = 1 - \left(\frac{\abs*{\frac{\sum_{i}^{n}\abs{x_{i} - y_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}}\right)
% \end{equation}

\begin{equation}
    CD_{(x,y)} = 1 - 2\left(\abs*{\frac{\sum_{i}^{n}\abs{x_{i} - y_{i}}}{n}-\frac{1}{2}}\right)
\end{equation}

\noindent Where $n$ is the number of taxa with comparable data and $x_i$ and $y_i$ are each characters states for the characters $x$ and $y$ and the taxa $i$.

@@

For any $n \in [1;\infty)$ and $x_{n}$ and $y_{n} \in (0,1)$ because the difference between character states is considered as Fitch-like (unordered; i.e. the difference between two different characters states is equal to $1$ and the difference between two identical character states is equal to $0$):

\begin{equation}
    \label{positive_demo}
    \begin{gathered}
    0 \leq  \abs{x_{n}-y_{n}} \leq 1\\
    0 \leq  \sum_{i=1}^{n}\abs{x_{i}-y_{i}} \leq n\\
    0 \leq  \frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n} \leq 1\\
    0 \leq  \abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}} \leq \frac{1}{2}\\
    0 \leq  2\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}} \leq 1\\
    0 \leq  1 - 2\left(\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}\right) \leq 1\\
    \end{gathered}
\end{equation}

@@

For any $n \in [1;\infty)$ and $x_{n} = y_{n}$ then:
%TG: Is that valid for a demonstration?
\begin{equation}
    \label{identitydemo}
    \begin{aligned}
    \abs{x_{n}-y_{n}} &= 0\\
    \sum_{i}^{n}\abs{x_{i}-y_{i}} &= 0\\
    \frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n} &= 0\\
    \abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}} &= \frac{1}{2}\\
    2\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}} &= 1\\
    1 - 2\left(\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}\right) &= 0\\
    \end{aligned}
\end{equation}

@@

\begin{equation}
    \label{equality_demo}
    \begin{aligned}
    \abs{x_{n}-y_{n}} &= \abs{y_{n}-x_{n}}\\
    \sum_{i}^{n}\abs{x_{i}-y_{i}} &= \sum_{i}^{n}\abs{y_{i}-x_{i}}\\
    \frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n} &= \frac{\sum_{i}^{n}\abs{y_{i}-x_{i}}}{n}\\
    \abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}} &= \abs*{\frac{\sum_{i}^{n}\abs{y_{i}-x_{i}}}{n}-\frac{1}{2}}\\
    2\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}} &= 2\abs*{\frac{\sum_{i}^{n}\abs{y_{i}-x_{i}}}{n}-\frac{1}{2}}\\
    1 - 2\left(\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}\right) &= 1 - 2\left(\abs*{\frac{\sum_{i}^{n}\abs{y_{i}-x_{i}}}{n}-\frac{1}{2}}\right)\\
    \end{aligned}
\end{equation}

@@

For any $n, j, b \in [1;\infty)$ and $x_{n}$, $y_{j}$, $z_{b}$ $\in (0,1)$:

\begin{equation}
    \label{subadditivity_demo}
    \begin{aligned}
    CD_{x,y} &\leq CD_{x,z} + CD_{z,y}\\
    \text{if:}\\
     1 - 2\left(\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}\right)
     &\leq 
     1 - 2\left(\abs*{\frac{\sum_{k}^{j}\abs{x_{k}-z_{k}}}{j}-\frac{1}{2}}\right) 
     +
     1 - 2\left(\abs*{\frac{\sum_{a}^{b}\abs{z_{a}-y_{a}}}{b}-\frac{1}{2}}\right) \\
     \text{then, the opposite is:}\\
     \underbrace{\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}} }_{\in[0,1/2]}
     &\geq 
     \underbrace{\abs*{\frac{\sum_{k}^{j}\abs{x_{k}-z_{k}}}{j}-\frac{1}{2}} }_{\in[0,1/2]}
     +
     \underbrace{\abs*{\frac{\sum_{a}^{b}\abs{z_{a}-y_{a}}}{b}-\frac{1}{2}} }_{\in[0,1/2]} - 2\\
     \text{thus:}\\
     \in[0,\frac{1}{2}] &\geq \in[0,\frac{1}{2}] + \in[0,\frac{1}{2}] -2 \\
     \in[0,\frac{1}{2}] &\geq \in[-2,-1]\\
    \end{aligned}
\end{equation}
